%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

% ----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://adhipk.dev/}{\Large Adhip Kashyap}} & Email : \href{mailto:adhip.kashyap@gmail.com}{adhip.kashyap@gmail.com}\\
%   \href{http://adhipk.dev/}{adhipk.dev} & Mobile : +1-602-515-5187 \\
%   \href{https://github.com/adhipk/}{github.com/adhipk}
%    & \href{https://linkedin.com/in/adhip-kashyap/}{linkedin.com/in/adhip-kashyap}\\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Adhip Kashyap} \\ \vspace{1pt}
    \small 602-515-5187 $|$ \href{mailto:adhip.kashyap@gmail.com}{\underline{adhip.kashyap@gmail.com}} $|$ 
    \href{https://linkedin.com/in/adhip-kashyap}{\underline{linkedin.com/in/adhip-kashyap}} $|$
    \href{https://github.com/adhipk}{\underline{github.com/adhipk}}
\end{center}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.1in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, SQL, PHP, Java, Go, C/C++, Scala, Rust} \\
     \textbf{Frameworks/Libraries}{: React, NextJs, Tailwind, D3.js, Flask, FastAPI, Apache Spark, Hadoop, Laravel, numPy, sciPy, openCV, PyTorch, TensorFlow, Hugging Face, XGBoost, pandas} \\
     \textbf{Developer Tools}{: Git, Docker, Google Cloud Platform, AWS, Sentry, PostHog, Drizzle, Kubernetes, Redis, Neo4j, Vapi} \\
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {AI Software Engineer}{Oct 2025 -- Present}
      {Hoag Hospital}{Orange County, CA}
      \resumeItemListStart
        \resumeItem{Engineered production AI call center agents handling autonomous appointment booking and patient communications at scale.}
        \resumeItem{Architected agent configuration management system using infrastructure-as-code principles with version control and automated deployment scripts across multiple environments.}
        \resumeItem{Designed and implemented CI/CD pipelines enabling continuous deployment of agent updates, \textbf{reducing deployment cycles by 80\%} and enabling rapid iteration.}
        \resumeItem{Built robust integrations with Epic EHR platform, enabling AI agents to autonomously manage imaging appointments while maintaining data integrity and HIPAA compliance.}
        \resumeItem{Developed order upload and review workflows bridging AI agents with human staff, establishing quality assurance processes and maintaining high accuracy standards.}
        \resumeItem{Led comprehensive compliance and adversarial testing program; engineered custom testing harnesses connected to Vapi voice platform for automated jailbreak evaluation and security assessment.}
        \resumeItem{Created intelligent test case generation system from phone transcripts, \textbf{accelerating regression testing cycles by 60\%}} and enabling data-driven quality metrics.}
      \resumeItemListEnd

    \resumeSubheading
      {Client Solutions Architect}{Apr 2025 -- Sep 2025}
      {TechAhead}{Thousand Oaks, CA}
      \resumeItemListStart
        \resumeItem{Architect scalable backend systems and enterprise infrastructure solutions, designing high-performance systems for mission-critical applications.}
        \resumeItem{Develop comprehensive cost proposals and technical roadmaps translating client requirements into strategic infrastructure recommendations.}
        \resumeItem{Design AI integration strategies that enhance application capabilities and create measurable business value for enterprise clients.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Aug 2024 -- Oct 2024}
      {Teaching Solved}{Tempe, AZ}
      \resumeItemListStart
        \resumeItem{Built comprehensive full-stack web application centralizing language learning resources, \textbf{improving user satisfaction by 25\%} and driving engagement metrics.}
        \resumeItem{Implemented advanced analytics instrumentation with PostHog, providing data-driven insights into user behavior and enabling product optimization that \textbf{increased customer retention by 30\%.}}
        \resumeItem{Engineered intelligent resource discovery system with optimized search and filtering, \textbf{reducing user research time by 2+ hours weekly} and improving conversion metrics.}
      \resumeItemListEnd
      


    \resumeSubheading
      {Software Engineering Intern}{May 2023 -- Aug 2023}
      {InduzBuy}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Engineered intelligent catalog normalization system leveraging GPT-3 and semantic similarity algorithms, achieving \textbf{95\% accuracy} in mapping diverse supplier product formats.}
        \resumeItem{Led architectural migration from legacy PHP to Laravel framework, establishing modular design patterns and significantly improving codebase maintainability and test coverage.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer}{Oct 2019 - Aug 2022}
      {ICICI Lombard}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Designed and deployed GraphDB-based decision engine using Neo4j and Python for dynamic insurance premium calculation, \textbf{delivering 40\% improvement} in system performance for calculation-intensive workflows.}
        \resumeItem{Led end-to-end redesign and development of customer renewal portal, architecting mobile-first responsive interface with ReactJS, \textbf{reducing checkout abandonment by 42\%} and driving significant revenue impact.}
        \resumeItem{Rapidly prototyped and launched mobile CRM application enabling remote field agent operations during COVID-19, \textbf{increasing team productivity by 30\%} and maintaining business continuity.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineer}{Jan 2019 - Oct 2019}
      {AutoNinja}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{Architected comprehensive error logging and monitoring infrastructure using Sentry, \textbf{reducing Mean Time to Repair (MTTR) by 40\%} through improved observability and incident response.}
        \resumeItem{Engineered real-time vehicle delivery tracking system providing customers with granular status updates, improving customer experience and reducing support inquiries.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Personal Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{LibriCasts} $|$ \emph{Python, Flask, Github Gists, htmx}}{Jan 2024 -- Mar 2024}
          \resumeItemListStart
          \resumeItem{Developed an open-source application to parse audiobook RSS feeds from Librivox.org and integrate them into PocketCasts.}
          \resumeItem{Resolved broken RSS feeds and deployed corrected versions via GitHub Gists for community use.}
          \resumeItem{Built a lightweight front end using Flask Templates and HTMX, ensuring a seamless user experience.}
          
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Data Processing Pipeline} $|$ \emph{Scala, Kubernetes, Hadoop, Apache Spark, neo4j}}{Jan 2023 -- May 2023}
          \resumeItemListStart
            \resumeItem{Developed a scalable data-processing pipeline to process spatial data using open NYC taxi Dataset.}
            \resumeItem{Performed hot-spot analysis using k-means and pageRank algorithms.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{catELMo TCR-Epitope Binding Affinity Prediction} $|$ \emph{PyTorch, Deep Learning}}{2023}
          \resumeItemListStart
            \resumeItem{Designed and trained a CNN to predict TCR-Epitope binding affinity using embeddings generated by catELMo, achieving \textbf{90\% accuracy} on the test set.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{LLM Science Exam} $|$ \emph{TensorFlow, DeBerta, RAG, Cohere APIs}}{2023}
          \resumeItemListStart
            \resumeItem{Trained a DeBerta-v2 LLM to answer STEM multiple-choice questions, implementing RAG system using Cohere APIs and TF-IDF for contextual retrieval, achieving \textbf{MAP@3 score of 0.92} on Kaggle competition test dataset.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Visual In-Context Learning Model} $|$ \emph{PyTorch, Contrastive Learning}}{2023}
          \resumeItemListStart
            \resumeItem{Implemented contrastive learning for feature extraction in Visual In-Context Learning using unsupervised and supervised retrievers, \textbf{improving model accuracy by 10\%}} over baseline on Pascal-5i dataset.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {Master's in Computer Science GPA: 3.6}{Aug 2022 -- May 2024}
    \resumeItemListStart
      \resumeItem{Relevant Coursework: Data Processing at Scale, Data Visualization, Data mining, Applied Cryptography }
    \resumeItemListEnd
    \resumeSubheading
      {PES University}{Bangalore, India}
      {B.Tech Mechanical Engineering; Minor's in Computer Science GPA 7.6/10}{Aug 2014 -- May 2018}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Data Structures, Database Management, Algorithms, Operating Systems}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%

 \section{Awards/Achievements}
 \resumeItemListStart
 \resumeItem{STAR Intern Award 2019 - Autoninja}
 \resumeItemListEnd


%-------------------------------------------
\end{document}
