%-------------------------
% Resume in Latex
% Author: Adhip Kashyap
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[sfdefault,light]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% defining link colour
% \definecolor{myPurple}{HTML}{866dbf}
% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that the generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}
% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://adhipk.dev/}{\Large Adhip Kashyap}} & Email : \href{mailto:adhip.kashyap@gmail.com}{adhip.kashyap@gmail.com}\\
  \href{https://www.linkedin.com/in/adhip-kashyap/}{linkedin.com/in/adhip-kashyap} & Mobile: \href{tel:+6025155187}{+1-602-515-5187} \\
  \href{https://adhipk.dev}{adhipk.dev}
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Tempe, AZ}
      {M.Sc in Computer Science; GPA: 3.6/4}{Aug 2022 -- May 2024}
    % \resumeSubheading
    %   {PES University}{Bengaluru, India}
    %   {B.Tech, Mechanical Engineering with Minors in Computer Science}{Aug 2015 -- July 2019}
  \resumeSubHeadingListEnd

%-----------Technical Skills----------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeItem
      {Languages}
      {C, C++, Python, JavaScript, SQL, PHP, Java, Go, Scala, Rust.}
    \resumeItem
      {Technologies/Frameworks}
      % {ReactJS, React Native, Redux, AngularJS, AWS, Flask, Laravel, Lumen, Spring, Springboot, Spring Data, PHPUnit, Pest,   neo4j, Redis, Docker, Sentry, nodeJS, ElasticSearch, Apache Spark, htmx, Vercel, Hadoop, Kubernetes, Vite, TailwindCSS, TailwindUI, AlpineJS, VueJS, SvelteJS, SolidJS, React Native, Next.js, GatsbyJS, NuxtJS, AstroJS, Bun, D3.js. }
      {Pytorch, Tensorflow, huggingface, ML, xgboost, LLMs, pandas, Numpy, D3.js, AWS, Flask, Redis, docker, neo4j, Vercel}
      % {AWS, Flask, Redis, Docker, neo4j, ElasticSearch, Apache Spark, Hadoop, Vercel, GCP. }
      
  \resumeSubHeadingListEnd
  
  
%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
        {InduzBuy}{Bengaluru, India}
        {Software Developer Intern}{June 2023 -- Aug 2023}
        \resumeItemListStart      
          \resumeItem{GPT-3 Customer Requirement Parser}{Built a script using GPT-3 and string similarity metrics to parse buyer requirements, normalize supplier catalogue data and find the best matches.}
          \resumeItem{Laravel Migration}{Spearheaded the migration of the existing code base from core PHP to Laravel --- introducing a streamlined Model-View-Controller architecture for improved modularity, scalability, and maintainability.}
        \resumeItemListEnd
    \resumeSubheading
      {ICICI Lombard}{Bengaluru, India}
      {Software Developer}{Oct 2019 -- Aug 2022}
      \resumeItemListStart
      \resumeItem{Renewals Portal}{
        % \begin{itemize}
        %   \item 
        Led the development team tasked with a major overhaul of the customer portal built on ReactJS and backend microservices in Lumen --- reducing renewal process time from 1 hour to under 10 minutes.
          % \item Developed internal debugging tools using ElasticSearch deployed on AWS Lambda to identify and rectify data entry errors. This aided in catching critical errors in the application configs.
        % \end{itemize}
      }
    \resumeItem{Rule Engine}
      {Created a GraphDB-based decision tree using Neo4j to compute key components of the insurance premium, improving load times by 40\% with significantly better maintainability by pruning redundant rules.}
      % {Wrote REST apis using SpringBoot to enable users add and modify existing rules, allowing stakeholders to quickly change configuration settings}

    \resumeItem{Microservices Migration}{
      Developed internal tools and implemented tests using AWS CloudWatch to monitor query times and cluster health for the Renewals platform.
      Worked on the migration of the monolith platform to smaller microservices built in Lumen which improved fault tolerance and scalability, enabling the system to accommodate significanlt more concurrent users.
    }
    % \resumeItem{Unit Test Development}{Wrote and maintained unit tests using Pest and PHPUnit to ensure modules worked as intended and to identify potential bugs and issues.}
        
    \resumeItem{Work From Home Solution}
      {Built a CRM mobile app during COVID-19 lockdowns using React Native and NodeJS, allowing customer relations executives to operate remotely using their phones.}
      
    \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {AutoNinja}{Bengaluru, India}
      {Software Developer}{Jun 2019 -- Oct 2019}
      \resumeItemListStart
        % \resumeItem {CRM Solution}{Developed APIs in Python/Flask and Laravel for the pre-sales CRM console, enabling automated report generation and enhanced business management for clients.}
        \resumeItem {Error Monitoring}{Implemented a custom error monitoring system using Sentry to track and resolve errors in the production environment, bringing the mean time to resolve from hours to 30 minutes.}
      \resumeItemListEnd

    \resumeSubSubheading
      {Technical Intern}{Jan 2019 -- Jun 2019}
      \resumeItemListStart
        \resumeItem{Event Management Portal}{Designed and implemented SQL tables and APIs in Laravel to create, manage, and track promotional events for clients. Built  a frontend in AngularJS enabling customers to access and download auto-generated reports.
        }
      \resumeItemListEnd
      \resumeSubHeadingListEnd
    

%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{catELMo TCR-Epitope Binding Affinity Prediction}
  {Designed and Trained a CNN to predict TCR-Epitope binding affinity using embeddings generated by catELMo, a bi-directional amino acid embedding model. The resulting model achieved an accuracy of 90\% on the test set.}
  \resumeSubItem{LLM Science Exam}
      {Trained a DeBerta-v2 LLM to answer STEM Multiple-choice questions as part of a Kaggle Competition. Implemented a RAG system using Cohere APIs and TF-IDF to provide the model with contextual information. Resulting Model had MAP@3 score of 0.92 on the competition test data set.}
  \resumeSubItem{Scalable Data Processing Pipeline}
      {Created a comprehensive data-processing pipeline to parse and analyse the open NYC taxi dataset using neo4j, Apache Spark, Hadoop, and Kubernetes.}
  \resumeSubItem{Visual In-context Learning Model }
    { Implemented contrastive learning for feature extraction in Visual In-Context Learning (ICL), using a two-stage process with unsupervised and supervised retrievers to select relevant demonstrations. Optimized retrieval performance through contrastive learning objectives, improving model transferability across downstream tasks. Resulted in a 10\% increase in accuracy over baseline in VOC the Pascal-5i dataset. }
    
    
    
    
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}

